---
title: "Your Paper Title Here"
author:
  - name: Author One
    affiliations:
      - name: Institution Name
        department: Department Name
        address: Address
        city: City
        country: Country
    email: author1@institution.edu
    orcid: 0000-0000-0000-0000
  - name: Author Two
    affiliations:
      - name: Another Institution
    email: author2@institution.edu
date: today
abstract: |
  This is the abstract of your paper. It should provide a concise summary of the background, methods, results, and conclusions of your research. Keep it to 150-250 words for most journals.
keywords:
  - keyword1
  - keyword2
  - keyword3
format:
  pdf:
    template-partials:
      - title.tex
---

# Introduction {#sec-introduction}

This is the introduction section. You can cite references like this [@example2024]. You can also cite multiple references [@example2024; @another2023].

Cross-references to sections work like this: see @sec-methods for details on the methodology.

# Methods {#sec-methods}

## Data Collection

Describe your data collection methods here.

## Statistical Analysis

### Analysis in R

Here's an example of an R code chunk that generates a figure:

```{r}
#| label: fig-example-r
#| fig-cap: "Example figure generated with R"
#| fig-width: 6
#| fig-height: 4

# Load libraries
library(ggplot2)

# Generate example data
set.seed(123)
data <- data.frame(
  x = rnorm(100),
  y = rnorm(100)
)

# Create plot
ggplot(data, aes(x = x, y = y)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_minimal() +
  labs(x = "Variable X", y = "Variable Y")
```

### Analysis in Julia

Here's an example of a Julia code chunk:

```{julia}
#| label: fig-example-julia
#| fig-cap: "Example figure generated with Julia"
#| eval: false

# using Plots
# using Random
#
# Random.seed!(123)
# x = randn(100)
# y = randn(100)
#
# scatter(x, y,
#         xlabel="Variable X",
#         ylabel="Variable Y",
#         legend=false,
#         alpha=0.6)
```

Note: Uncomment the Julia code above when you have the required packages installed.

## Creating Tables

Here's an example table:

```{r}
#| label: tbl-example
#| tbl-cap: "Summary statistics"

library(knitr)

results <- data.frame(
  Metric = c("Mean", "SD", "N"),
  Group_A = c(10.5, 2.3, 50),
  Group_B = c(12.1, 2.8, 50)
)

kable(results, format = "markdown", align = c("l", "r", "r"))
```

# Results {#sec-results}

Present your results here. You can reference figures like @fig-example-r and tables like @tbl-example.

Key findings:

- Finding 1
- Finding 2
- Finding 3

# Discussion {#sec-discussion}

Discuss your findings in the context of existing literature.

## Limitations

Describe the limitations of your study.

## Future Directions

Suggest directions for future research.

# Conclusions {#sec-conclusions}

Summarize the main conclusions of your work.

# Acknowledgments {.unnumbered}

This section is optional. Acknowledge funding sources and collaborators here.

# References {.unnumbered}

::: {#refs}
:::

# Supplementary Materials {.unnumbered}

If you have supplementary materials, describe them here.
