---
title: "Your Paper Title Here"
author:
  - name: Your Name
    affiliation: Your Institution
    email: your.email@institution.edu
date: today
abstract: |
  This is where you write your abstract. Keep it concise (typically 150-300 words).
  Summarize your research question, methods, key findings, and conclusions.
bibliography: references.bib
---

# Introduction

Your introduction goes here. Cite sources using `[@citation_key]` for parenthetical citations or `@citation_key` for in-text citations [@example2024].

You can reference equations like @eq-example, figures like @fig-example, and tables like @tbl-example.

## Research Question

State your research question or hypothesis here.

# Methods

Describe your methodology here.

## Data

Describe your data sources and collection methods.

## Analysis

You can include R code chunks to perform analysis:

```{r}
#| label: fig-example
#| fig-cap: "Example figure caption"
#| echo: false

# Example R code
x <- 1:10
y <- x^2
plot(x, y, main="Example Plot", xlab="X values", ylab="Y values")
```

You can also include equations:

$$
y = \beta_0 + \beta_1 x + \epsilon
$$ {#eq-example}

# Results

Present your findings here.

```{r}
#| label: tbl-example
#| tbl-cap: "Example table caption"
#| echo: false

# Example table
knitr::kable(data.frame(
  Variable = c("X", "Y", "Z"),
  Mean = c(1.5, 2.3, 3.1),
  SD = c(0.5, 0.7, 0.6)
))
```

# Discussion

Interpret your results and discuss implications.

## Limitations

Discuss limitations of your study.

## Future Work

Suggest directions for future research.

# Conclusion

Summarize your key findings and their significance.

# References

::: {#refs}
:::

# Appendix {.appendix}

## Computational Environment

```{r}
#| label: session-info
#| echo: false

sessionInfo()
```
